Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-03-11 paper.tex
Minor fix
Add data availability
Add Matthes papaer

To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq.~\ref{eq:def-eps-2} with $L$ we obtain the sheet polarization density

@@

$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, 
which is independent of $L$ due to the locality 
of $\boldsymbol{u}$ and $A$. 

@@

(Fig. \ref{fig-1}\textbf{d}-\textbf{e}}).

@@

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.74\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. \textbf{a}. The structures of
  the 2D materials investigated in this
  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. \textbf{c}.
  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. \textbf{d}.
  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with slope very
  close to $1/4\pi$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
  as superimposed on \textbf{c} and \textbf{d}.}
\end{figure}

>>>>

To solve this problem, we need to find the $L$-independent alternative
of $\varepsilon_{\mathrm{SL}}$, which is related to both electrostatic
and optical properties of a 2D material \cite{Matthes_2016}. As
described before, by multiplying Eq.~\ref{eq:def-eps-2} with $L$ we
obtain the sheet polarization density

@@

$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, which is
independent of $L$ due to the locality of $\boldsymbol{u}$ and $A$.

@@

(Fig. \ref{fig-1}\textbf{d}-\textbf{e}).

@@

\section{Data Availability}
The data that support the findings of this study are available from
the corresponding author upon reasonable request.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. \textbf{a}. The structures of
  the 2D materials investigated in this
  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. \textbf{c}.
  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. \textbf{d}.
  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with slope very
  close to $1/4\pi$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using the data from Ref.~\citenum{Haastrup_2018} (squares),
  as superimposed on \textbf{c} and \textbf{d}.}
\end{figure}
